---
title: "My R Markdown Primer"
author: "Killian Williams"
date: "2025-11-12"
output:
  pdf_document: default
  html_document: default
---
## Explantion

R Markdown is like Python's Jupyter. Its great for exploratory Data Science/Analytics reports. The graphs and statistical computation needs an explanation as to how this can explain an observed pattern.


$$
\alpha^2 + \beta^2 = \gamma^2
$$
## Narrative

Below is the setup and plotting of data in ggplot2. The plot clearly shows a Linear Negative Relationship between MPG and Weight. With this graph we can confidently assume that the more heavier a vehicle is the slower it will be. Further analysis is still needed to get a wider view of the mtcars dataset.


```{r setup}
install.packages("tinytex")
library(ggplot2)
car <- mtcars

```



```{r cars}
ggplot(car, aes(x=wt, y=mpg, color=mpg)) + geom_point() + labs(x='Weight in Tons', y='Miles Per Hour', title='Linear Negative graph')
```

## Conclusion

Using markdown is far more convenient compared to a simple report. Markdown has all of the features needed to create a coherent report. For example, a Cell (created by using ctrl+alt+i) can not only execute code but they can also individually run separately, can be changed in the setting features etc. I would always prefer this over any simple word document.

